---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SumProductVE

<!-- badges: start -->
<!-- badges: end -->

The goal of SumProductVE is to perform exact inference in Bayesian Networks.
The package contains an implementation of the factor-product and 
Sum-Product-VE algorithm given in Koller (2009), for exact inference 
in discrete Bayesian Networks. The factor-product procedure is implemented in Rcpp
for speed and can be applied to factors (conditional probability tables, CPTs) 
represented as multidimensional arrays (as in the bnlearn-package).

## Installation

You can install the development version of SumProductVE from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("verahk/SumProductVE")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SumProductVE)

## basic example code
new_factor <- function(val, dim, scope) array(val, dim, setNames(vector("list", length(dim)), scope))
z <- new_factor(c(.5, .5), 2, "z")
x <- new_factor(c(0, 1),  2, "x")
y <- new_factor(c(.1, .9,
                  .2, .8,
                  .3, .7,
                  .4, .6), c(2, 2, 2), c("y", "x", "z"))

factor_product(list(x, y, z))  # joint distribution
sum_product_ve(list(x, y, z), elim = character(0))  # same
sum_product_ve(list(x, y, z), elim = "y")           # marginal distribution of x and y
```

## Example 2: cpquery from list of CPTs
```{r}
cpts <- list(z = z, x = x, y = y)
cpquery(cpts, y = "y")
```

## Example 3: 
```{r}
g <- bnlearn::empty.graph(names(cpts))
bnlearn::amat(g) <- dag_from_cpts(cpts)
bn <- bnlearn::custom.fit(g, cpts)
bn 

cpquery(bn, "y")
```

